Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-06 paper/flairs27/content/results.tex
More cleanup

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was developed on a 32-core server described in Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations, 4 months of data (October 2011 - February 2012) is for training purposes. This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size. Some of the documents have null values for their annotation fields. The first portion of the data which ranges from October 2011 to February 2012 is considered as training data. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

@@

We have 135 extraction patterns covering each slot-name/entity-type combinations. Our final submission was named \textit{submission\_infer}. Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference. Slot extraction using patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.

@@

\begin{table}
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}

@@

\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|c|c|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|p{13mm}|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

>>>>

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 The purpose of evaluation is to measure the effectiveness of extracting slot values for various entities, metrics such as precision and recall would be considered. We perform random samplings to extract these. Our system was developed on a 32-core server described in Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations. The first four months of data (October 2011 - February 2012) is for training purposes, and we use this portion to lookup sample lines and for system parameter settings purposes. This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size. Some of the documents have null values for their annotation fields. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

@@

We have 172 extraction patterns covering each slot-name/entity-type combinations. Our final submission was named \textit{submission\_infer}. Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference. Slot extraction using patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.

@@

\begin{table}
\caption{Initial Performance Measure }
\centering
\label{table:initialresult}

@@

\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|c|c|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\caption{Accuracy Measure: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|p{13mm}|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

### 2013-11-06 paper/flairs27/content/system.tex
Fix Table width
Some table moving arounds
More cleanup

\begin{figure}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=3in]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

@@

\subsection{Wikipedia Citation}
The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have a low chance of being citable in Wikipedia. So we take on that and ignore non-citing documents.

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Document Chunks Indexer} and \textit{Document Filter}. Document chunks Indexer will generate indexes of the chunk files that contain a mention of any of the desired entities. Document Filter on the other hand will index documents that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every chunk file/document for every entity. The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible. Document Chunks Indexer which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there. Each chunk file can contain up to thousands of documents which can be so time consuming if we were to process them in our Java base code. Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{http://alias-i.com/lingpipe/}. Then use these senteces to match patterns and when patterns matched, generate SSF results.

@@

The first value, $p_1$ represents the type of entity. These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person. \texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types. The $p_2$ represents a slot name. A list of slot names is present in Table~\ref{table:slotNameOntology}. The third element $p_3$ is the pattern content. This is a string found in the sentence. The extractor looks for this exact string or pattern in a sentence. The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence. The final element $p_5$ represent the slot value of a pattern. This %When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we explain the patterns with more details, an example can be found in Figure~\ref{fig:pattern}.

@@

The SSF output of streaming slot value extraction is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present at this stage. The input file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. We define two classes of rules: \textit{deduplication} and \textit{inference} rules.

@@

\subsubsection{A short discussion}

>>>>

\begin{figure}
\hspace{-10mm}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

@@

\subsection{Wikipedia Citation}
The main goal of this section is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is that there have been observations of how non-mentioning documents have a low chance of being citable in Wikipedia \cite{JFrank12}. So we take on that and ignore non-citing documents.

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Document Chunks Indexer} and \textit{Document Filter}. The purpose of these indexes is to reduce I/O cost while generating slot values for various entities. Document chunks Indexer will generate indexes of the chunk files that contain a mention of any of the desired entities. Document Filter on the other hand will index documents that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every chunk file/document for every entity. The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible. Document Chunks Indexer which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there. Each chunk file can contain up to thousands of documents which can be so time consuming if we were to process them in our Java base code. Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{Lingpipe (available in the dataset) provides entity tags and in-document correference. http://alias-i.com/lingpipe/}. Then use these senteces to match patterns and when patterns matched, generate SSF results.

@@

The first value, $p_1$ represents the type of entity. These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person. \texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types. The $p_2$ represents a slot name. A list of slot names is present in Table~\ref{table:slotNameOntology}. The third element $p_3$ is the pattern content. This is a string found in the sentence. The extractor looks for this exact string or pattern in a sentence. The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence. The final element $p_5$ represent the slot value of a pattern. This %When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP\footnote{OpenNLP was used for part of speech tagging. http://opennlp.apache.org/‎} or a hard-coded phrase. For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we explain the patterns with more details, an example of which can be found in Figure~\ref{fig:pattern}.

@@

The output of streaming slot value extraction is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present at this stage. The input file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. We define two classes of rules: \textit{deduplication} and \textit{inference} rules.

@@
